Universal Anonymous Signatures

### 2022-07-18 prism-backend/research/gsac/formal-uas.tex
Applying comments by Markulf.

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given \parm, and the
  function \fissue for checking that credential requestors meet the conditions
  to be issued a credential, an issuer runs \IKeyGen to generate its issuing key
  pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given \parm, returns a user's secret
  key.
\item[$\langle
  \Obtain(\usk,\ipk,\sCred,\attrs),
  \Issue(\isk,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,\utrans/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$ from an
  issuer in the system, where \cid is a unique identifier for the credential,
  \ipk is the issuer's public key and \cred is the actual credential, on
  attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i,\cattrs_i,\cred_i,\ipk_i)
  \rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for readability. The
  user outputs the produced credential \Cred, while the issuer outputs the
  corresponding protocol transcript \utrans.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\usk,\attrs,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]})
  \rightarrow 0/1$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with secret key \usk,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where $n$
  may be $0$ if no previously obtained credential is used). \fissue returns $1$
  to accept a request, $0$ to reject it.
\item[$\feval: (\usk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user secret key \usk, a set of credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n \ge 1$), and the message to be signed \msg. \feval outputs two values,
  $\yeval^0$ and $\yeval^1$, which can be used to modulate the bevahiour of
  \finsp, and must belong in a well defined set \rngfeval. For readability, we
  write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\usk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},\msg)
  \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

@@

\begin{definition}{(\UAS-acceptable functions)}
  \label{def:uas-acc-func}
  We say that a \fissue (similarly, \feval or \finsp) function chosen from some
  family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
  is one-way with respect to \usk. That is, given the output of \fissue
  (similarly, \feval or \finsp), it is at least computationally unfeasible to
  recover the \usk value used to produce it.
\end{definition}

@@

We define the security expected from an \UAS scheme using a game-based approach.
An \UAS scheme must ensure privacy at credential issuance, meaning that two
runs of the credential issuance protocol should not leak any information beyond
necessary about the user requesting the credential. Note that this is now
crucial for privacy since, as AC schemes, \UAS allows multiple credentials per
user -- thus, knowing what user is requesting which credential can lead to user
profiling. It must also ensure signature privacy, meaning that no information
can be learned by third parties from a signature, beyond what the user chooses
to reveal, and what may be extractable by the chosen opener. Issuance
unforgeability requires that \UAS schemes ensure that the claims used to support
a credential request cannot be falsified (issuance unforgeability). Similarly,
signature unforgeability requires that no adversary should be able to falsify
the correctness proofs for the claims included in the signatures. In both cases
(issuance and signature unforgeability), we require all credentials involved in
the corresponding process to be associated to a known user. Finally, \UAS
schemes inherit the useful non-frameability property of GS schemes where even
the issuer is corrupt. In this case, we can ensure that no honest user
can be framed with having created a signature that s/he did not create --
although the concept may get a bit blurred, as there is no traditional opening.
%
We describe next the global variables and oracles that we use in our modelling.

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
for issuers, \iid; and for openers, \oid. % In all cases, we use bold font to
% denote sets: e.g., \scid and \siid denote sets of credential and issuer
% identifiers. All tables/sets are initialized as empty tables/sets.

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of honest users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of corrupt users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.    
\item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
  user, we use $\UK[\uid]$. 
\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
  use \PUBIK to refer to the public component, which also includes the \fissue
  function; and \PRVIK refers to the private component of the key pair.
\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
  of \fissue, \OK includes the \finsp function.
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$ to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
  issuance anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$''. We
  may also use \OWNR over a set of {\cid}s (\scid). In that case, our convention
  is that $\OWNR[\scid]$ returns $\bot$ if not all passed {\cid}s belong to the
  same \uid.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

        \procedure{$\HUGEN(\uid)$}{%
          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
          \usk \gets \UKeyGen(\parm) \\
          \UK[\uid] \gets \usk;
          \HU \gets \HU \cup \lbrace  \uid \rbrace \\
          \pcreturn \top \\
        }

@@

        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
          \rbrace_{i \in [n]})$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \HI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
          \pcreturn \bot \\
          \langle \Cred, \utrans \rangle \gets
          \langle \Obtain(\UK[\uid],\CRED[\lbrace \cid_i\rbrace_{[n]}],\attrs), \\
          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\lbrace \cid_i\rbrace_{[n]}],\attrs)
          \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, n,
          \lbrace(\cid_i,\iid_i)\rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

@@

        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1})$}{%
          \textrm{\todo{\scid notation}} \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),\adv \rangle \\
          \CCRED[\ccid_b] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1},\msg,\feval)$}{%
          \textrm{\todo{\scid notation}} \\                    
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \pcfor d \in \bin~ \exists \cid,\cid' \in \scid_d~\suchthat \\
          \pcind \cid \in \CRED \land \cid' \in \CCRED: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\UK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
          \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\cscid_b,\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\cscid_{1-b},\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global (simulated) parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\usk,\sCred=
  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
  and returns the credential set \sCred, if any, involved in the request. It
  needs an honest issuer as, otherwise, the transcripts won't be available. 
\item[$\ExtractSign(\trap,\oid,\lbrace \iid_i \rbrace_{i \in [n]},\Sig,\msg,
  \feval) \rightarrow (\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
  \Sig, as well as the opener identifier \oid, and the identifiers of all
  issuers of the credentials used to produce the signature over \msg, and for
  \feval. It outputs the user secret key and credential set \sCred used to
  generate the signature, and the $\yeval^1$ and \yinsp values.
% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
%   $0$.

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.}
  \label{fig:nizkrels}
\end{figure}

Note that, besides the extensibility introduced via \fissue, \feval and
\finsp, some aspects of the previous functions could be modified (e.g., one
could require issuer public keys to be kept private). However, the previous
relations seem generic enough for a wide variety of applications.
%
From them, we build \CUASGen as follows.

>>>>

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given \parm, and the
  function \fissue for checking that credential requestors meet the conditions
  to be issued a credential, an issuer runs \IKeyGen to generate its issuing key
  pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
  key pair.
\item[$\langle
  \Obtain(\usk,\ipk,\sCred,\attrs),
  \Issue(\isk,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,\utrans/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$ from an
  issuer in the system, where \cid is a unique identifier for the credential,
  \ipk is the issuer's public key and \cred is the actual credential, on
  attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i,\cattrs_i,\cred_i,\ipk_i)
  \rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for readability. The
  user outputs the produced credential \Cred, while the issuer outputs the
  corresponding protocol transcript \utrans.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\fissue: ((\upk,\usk),\attrs,\lbrace (\cid_i,\cattrs_i)
  \rbrace_{i \in [n]}) \rightarrow 0/1$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with key pair $(\upk,\usk)$,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where $n$
  may be $0$ if no previously obtained credential is used). \fissue returns $1$
  to accept a request, $0$ to reject it.
\item[$\feval: ((\upk,\usk),\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user key pair $(\upk,\usk)$, a set of credentials with identifiers
  and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$, which can be used to modulate the bevahiour
  of \finsp, and must belong in a well defined set \rngfeval. For readability,
  we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,(\upk,\usk),\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

@@

\begin{definition}{(\UAS-acceptable functions)}
  \label{def:uas-acc-func}
  We say that a \fissue (similarly, \feval or \finsp) function chosen from some
  family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
  is one-way with respect to $(\upk,\usk)$. That is, given the output of \fissue
  (similarly, \feval or \finsp), it is at least computationally unfeasible to
  recover the $(\upk,\usk)$ value used to produce it.
\end{definition}

@@

We define the security expected from an \UAS scheme using a game-based approach.
An \UAS scheme must ensure privacy at credential issuance, meaning that two
runs of the credential issuance protocol should not leak any information beyond
necessary about the user requesting the credential. Note that this is now
crucial for privacy since, as AC schemes, \UAS allows multiple credentials per
user -- thus, knowing what user is requesting which credential can lead to user
profiling. It must also ensure signature privacy, meaning that no information
can be learned by third parties from a signature, beyond what the user chooses
to reveal, and what may be extractable by the chosen opener. Issuance
unforgeability requires that \UAS schemes ensure that the claims used to support
a credential request cannot be falsified (issuance unforgeability). Similarly,
signature unforgeability requires that no adversary should be able to falsify
the correctness proofs for the claims included in the signatures. In both cases
(issuance and signature unforgeability), we require all credentials involved in
the corresponding process to be associated to a known user key. Finally, \UAS
schemes inherit the useful non-frameability property of GS schemes where even
the issuer is corrupt. In this case, we can ensure that no honest user
can be framed with having created a signature that s/he did not create --
although the concept may get a bit blurred, as there is no traditional opening.
%
We describe next the global variables and oracles that we use in our modelling.

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
for issuers, \iid; and for openers, \oid.  In all cases, we use bold font to
denote sets: e.g., \scid and \siid denote sets of credential and issuer
identifiers. All tables/sets are initialized as empty tables/sets. For
notational convenience, we often use these identifiers instead of the
corresponding user/issuer/opener keys.

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of honest users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of corrupt users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.    
\item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$. To
  refer to the key of a specific user, we use $\UK[\uid]$. \PUBUK indexes the
  public keys, and \PRVUK the private keys.
\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
  use \PUBIK to refer to the public component, which also includes the \fissue
  function; and \PRVIK refers to the private component of the key pair.
\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
  of \fissue, \OK includes the \finsp function.
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$ to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
  issuance anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$''. We
  may also use \OWNR over a set of {\cid}s (\scid). In that case, our convention
  is that $\OWNR[\scid]$ returns $\bot$ if not all passed {\cid}s belong to the
  same \uid.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

        \procedure{$\HUGEN(\uid)$}{%
          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
          (\upk,\usk) \gets \UKeyGen(\parm) \\
          \UK[\uid] \gets (\upk,\usk);
          \HU \gets \HU \cup \lbrace  \uid \rbrace \\
          \pcreturn \top \\
        }

@@

        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
          \rbrace_{i \in [n]})$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \HI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
          \pcreturn \bot \\
          \langle \Cred, \utrans \rangle \gets
          \langle \Obtain(\UK[\uid],\CRED[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs), \\
          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs)
          \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, n,
          \lbrace(\cid_i,\iid_i)\rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

@@

        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=
          \lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),\adv \rangle \\
          \CCRED[\ccid_b] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1}=
          \lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\UK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
          \pcreturn \bot \\          
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\cscid_b,\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\cscid_{1-b},\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\begin{description}
\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
  parameter, outputs global (simulated) parameters \parm whose distribution is
  indistinguishable to that produced by the \Setup algorithm, as well as a
  trapdoor \trap.
\item[$\ExtractIssue(\trap,\utrans) \rightarrow ((\upk,\usk),\sCred=
  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
  and returns the credential set \sCred, if any, involved in the request. It
  needs an honest issuer as, otherwise, the transcripts won't be available. 
\item[$\ExtractSign(\trap,\oid,\lbrace \iid_i \rbrace_{i \in [n]},\Sig,\msg,
  \feval) \rightarrow ((\upk,\usk),\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
  \Sig, as well as the opener identifier \oid, and the identifiers of all
  issuers of the credentials used to produce the signature over \msg, and for
  \feval. It outputs the user secret key and credential set \sCred used to
  generate the signature, and the $\yeval^1$ and \yinsp values.
% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
%   $0$.

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.
  \todo{Is $\C = \CCommit(\usk;r)$ needed now that \upk is added?}}
  \label{fig:nizkrels}
\end{figure}

From them, we build \CUASGen as follows.
